\usemodule[m-cv]

\starttext

\CVTITLE{Dan Huy}{Nguyen}
\CVSUBTITLE{\LINK{danhuynguyen1@gmail.com}{mailto:danhuynguyen1@gmail.com} \| \LINK{LinkedIn}{https://www.linkedin.com/in/dan-nguyen-857282190/} \| \LINK{CV}{https://gitlab.com/dennuguyen/curriculum-vitae/-/blob/master/cv.pdf} \| \LINK{GitLab}{https://gitlab.com/dennuguyen} }

\CVSECTION{Education}
    \CVHEADING{University of New South Wales}{Feb 2018 -- Dec 2023}
        \CVSUBHEADING{Bachelor of Engineering (Hons) (Mechatronics) / Bachelor of Science (Computer Science)}{}
        \startitemize
            \item Cumulative WAM of 81.758.
            \item Notable courses: DESN2000(99), ENGG3600 (94), MATH2019 (93).
        \stopitemize

\CVSECTION{Work Experience}
    \CVHEADING{UNSW}{}
        \CVSUBHEADING{Casual Academic}{Sep 2021 -- Current}
        \startitemize
        \item Lab demonstrator for first-year to post-graduate engineering courses (DESN1000, MTRN2500, MTRN3100, MTRN4110, COMP9024) with an average satisfaction rate of 95\%.
        \item Course planner for robotics courses (MTRN2500, MTRN3100, MTRN4231) involving curriculum development and creation of teaching content for labs and assessments.
        \stopitemize

\CVSECTION{Project Experience}
    \CVHEADING{Sumobots}{May 2022 -- July 2022}
        \startitemize
            \item Organised team to deliver 1\high{st} place winning sumobot in MTRNSoc x CREATE Sumobots Competition Advanced Stream.
            \item Participated in concept generation of solution and requirements.
            \item Soldered and assembled electrical system.
            \item Implemented robot software architecture and control loop.
        \stopitemize

    \CVHEADING{UNSW Competitive Robotics Group}{Sep 2021 -- June 2022}
        \startitemize
            \item Created ROS control, description, and gazebo packages for end effector and combined UAV/end effector robots.
            \item Modelled CAD artefacts with URDF/Xacro/SDF for Gazebo simulation.
        \stopitemize

    \CVHEADING{Offworld Robotics}{}
        \CVSUBHEADING{Project Manager}{Dec 2020 -- June 2022}
        \startitemize
            \item Supervision of a leadership team to conduct operations with respect to project management plan and systems engineering management plan.
            \item Centralisation and refinement of processes, structures, documentation, and workflows onto GitLab to improve organisational efficiency and standardise quality.
        \stopitemize

        \CVSUBHEADING{Mechanical \& Manufacturing Student Engineer}{Jan 2020 -- Dec 2020}
        \startitemize
            \item Designed ladder-frame chassis, bogie suspension, and limited-slip differential under a hybrid agile-waterfall design process for rapid iteration and 3D-printing manufacturing.
            \item Simulated and optimised parts in various loading conditions with FEA.
            \item Invented unique differential as proof-of-concept of kinematic mechanisms for integration with bogie suspension.
        \stopitemize

\CVSECTION{Competition Experience}
    \CVHEADING{Accenture Technology Bootcamp}{Feb 2022}
    \startitemize
        \item Developed a proof-of-concept "GitLab Team Management" application in Django/Python connecting to GitLab API to enhance people management capabilities.
    \stopitemize

    \CVHEADING{WIESoc x IBM Hackathon}{Oct 2020}
    \startitemize
        \item Developed prize-winning "COVID Safe Link" website in Flask/Python connecting to Google Maps API and NSW Open Data Platforms to plan safe travel through populated areas and public transport.
    \stopitemize

\stoptext