\usemodule[m-cv]

\starttext

\CVTITLE{Dan Huy}{Nguyen}
\CVSUBTITLE{\LINK{danhuynguyen1@gmail.com}{mailto:danhuynguyen1@gmail.com} \| 0421 720 990 \| \LINK{LinkedIn}{https://www.linkedin.com/in/dan-nguyen-857282190/} \| \LINK{GitLab}{https://gitlab.com/dennuguyen} \| \LINK{GitHub}{https://github.com/dennuguyen} }

% \CVSECTION{Summary}
%     I love challenges and doing well.
%     \blank[big]

\CVSECTION{Education}
    %!!! [swe]
    \CVHEADING{University of New South Wales}{Feb 2018 -- April 2024}
        \CVSUBHEADING{Bachelor of Engineering (Hons) (Mechatronics) / Bachelor of Science (Computer Science)}{}
        \startitemize
            \item Graduated 1st class.
            \item Total weighted average mark of 82.622.
        \stopitemize

    \CVHEADING{Patrician Brothers' College Fairfield}{Oct 2017}
        \CVSUBHEADING{Higher School Certificate}{}
        \startitemize
            \item ATAR of 94.25.
            \item Subjects: Extension 2 Mathematics, Extension 1 Mathematics, Chemistry, Physics, English Advanced.
        \stopitemize

\CVSECTION{Work Experience}
    %!!! [swe]
    \CVHEADING{Accenture}{}
        \CVSUBHEADING{Application Development Analyst}{May 2024 -- Current}
        \startitemize
            \item Configuring and testing CRM in public sector with Salesforce and Azure DevOps.
        \stopitemize

    %!!! [swe]
    \CVHEADING{UNSW}{}
        \CVSUBHEADING{Casual Academic}{Sep 2021 -- Current}
        \startitemize
            \item Involved in planning course curriculum and content from assessments to lectures for C++ and robotics courses across all year levels.
            \item Taught and mentored classes, ran help sessions, and marking for engineering design, robotics, and C++ courses.
            \item Lead migration for delivery of course content using GitHub Classrooms.
            \item Optimise processes using scripting, build tools, CI/CD tools.
            \item List of courses taught for: DESN1000, DESN2000, MTRN2500, MTRN3100, MTRN4110, COMP9024.
            \item List of courses administrated for: MTRN2500, MTRN3100, MTRN4231.
        \stopitemize

    \CVHEADING{Sperospace}{}
        \CVSUBHEADING{Mechanical Engineering Intern}{Jul 2021 -- Oct 2021}
        \startitemize
            \item Conceptual design of end effector (technology readiness level 3) for use in space applications using engineering concept design tools.
        \stopitemize

\CVSECTION{Project Experience}
    %!!! [swe]
    \CVHEADING{Social Media App}{August 2024 -- Current}
        \CVSUBHEADING{Fullstack Developer}{}
        \startitemize
            \item Designed social media mobile app that is cross between popular Dress To Impress Roblox game and BeReal.
            \item Implemented with Flutter + Firebase (Functions, Firestore, Storage, Authentication, AppCheck), Google & Apple social authentication, and custom camera and gallery picker.
        \stopitemize

    %!!! [swe]
    \CVHEADING{TV Mate}{May 2024 -- June 2024}
        \CVSUBHEADING{Application Developer}{}
        \startitemize
            \item Designed and implemented Flutter mobile app with mDNS-enabled IR-firing IoT devices (ESP8266) for remote control of multiple TVs via websockets over LAN.
        \stopitemize

    %!!! [swe]
    \CVHEADING{Split Payment App}{Sep 2023 -- Current}
        \CVSUBHEADING{Application Developer}{}
        \startitemize
            \item Solely prototyping multiplayer split-payment app with fractional splitting enabled by multi-range sliders and OCR for receipt-digitisation.
            \item Built with Firebase, Firestore, React, Mantine UI, Tabler, immer, react-slider, tesseract.js, wouter, zustand, Vite, Vitest.
        \stopitemize

    \CVHEADING{Sumobots}{}
        \CVSUBHEADING{Sumoltaneous Equations}{May 2022 -- July 2022}
        \startitemize
            \item Organised team and delegated WBS (waterfall) to deliver 1\high{st} place winning sumobot in MTRNSoc x CREATE Sumobots Competition Advanced Stream.
            \item Participated in concept generation of solution and requirements.
            \item Soldered and assembled electrical system.
            \item Architected robot software design and control loop.
        \stopitemize

    \CVHEADING{UNSW Competitive Robotics Group}{}
        \CVSUBHEADING{Robotics Student Engineer}{Sep 2021 -- June 2022}
        \startitemize
            \item Created ROS control, description, and gazebo packages for end effector and combined UAV/end effector robots.
            \item Modelled CAD artefacts with URDF/Xacro/SDF for Gazebo simulation.
            \item Assisting project management with MS Teams management and WBS development.
        \stopitemize

    \CVHEADING{Offworld Robotics}{}
        %!!! [swe]
        \CVSUBHEADING{Project Manager}{Dec 2020 -- June 2022}
        \startitemize
            \item Supervised leadership team to conduct operations with respect to project management plan and systems engineering management plan.
            \item Centralisation and refinement of processes, structures, documentation, and workflows onto GitLab to improve organisational efficiency and standardise quality.
            \item Developed learning curriculum covering design and implementation of robotic systems for upskilling of Offworld Robotics students.
        \stopitemize

        \CVSUBHEADING{Mechanical \& Manufacturing Student Engineer}{Jan 2020 -- Dec 2020}
        \startitemize
            \item Designed ladder-frame chassis, bogie suspension, and limited-slip differential with hybrid agile-waterfall design process for rapid iteration and 3D-printing manufacturing.
            \item Simulated and optimised parts in various loading conditions with FEA.
            \item Invented unique differential as proof-of-concept of kinematic mechanisms for integration with bogie suspension.
        \stopitemize

% \CVSECTION{Extracurricular}
    

\CVSECTION{Competition Experience}
    %!!! [swe]
    \CVHEADING{Accenture Technology Bootcamp}{Feb 2022}
    \startitemize
        \item Developed proof-of-concept "GitLab Team Management" application in Django/Python connecting to GitLab API to enhance people management capabilities.
    \stopitemize

    %!!! [swe]
    \CVHEADING{WIESoc x IBM Hackathon}{Oct 2020}
    \startitemize
        \item Developed prize-winning "COVID Safe Link" website in Flask/Python connecting to Google Maps API and NSW Open Data Platforms to plan safe travel through populated areas and public transport.
    \stopitemize

    \CVHEADING{WIESoc x Aurecon Design Challenge}{Sep 2019}
    \startitemize
        \item Conceptualised an innovative solution to assist unconfident and learning drivers in adapting to high-speed lane mergers and intersection turns.
    \stopitemize

\CVSECTION{Volunteer Experience}
    \CVHEADING{CSESoc Peer Mentoring}{}
        \CVSUBHEADING{Peer Mentor}{Feb 2022 -- May 2022}
        \startitemize
            \item Assist students transition into university life with degree plan strategy.
            \item Help students setup development environments e.g. SSH, VSCode, and C build tools.
        \stopitemize

    \CVHEADING{Engineering World Health Summer Institute}{}
        \CVSUBHEADING{Biomedical Equipment Technician}{Dec 2018 -- Feb 2019}
        \startitemize
            \item Trained in student volunteer program in Cambodia with acquired skills in soldering, mechanical and electrical repairs of biomedical equipment.
            \item Repaired and returned to service twenty-seven hospital equipment in four-week rural hospital placement.
            \item Built AC-to-DC rectifier to extensively test electrical circuits of biomedical equipment.
        \stopitemize

\CVSECTION{Academic Projects}
    \CVHEADING{MMAN4010/4020 -- Thesis A/B}{May 2023 -- Dec 2023}
    \startitemize
        \item Lead team of students to build proof-of-concept website for real client to achieve course marks of 95 and 89.
        \item Architected system which was a website integrated with a mechatronic system to automate control of multiple TVs using websockets over WiFi.
    \stopitemize

    %!!! [swe]
    \CVHEADING{COMP6080 -- Web Front-End Programming}{May 2023 -- Dec 2023}
    \startitemize
        \item Built frontend Airbnb clone (using React, Mantine, SWR, Axios, Wouter, Zustand) given a backend API to achieve course mark of 90.
        \item Built frontend web messaging platform (in pure vanilla JS, HTML, CSS, and Bootstrap) given a backend API and using Web APIs like HTML DOM, Intersection Observer, and Navigation.
    \stopitemize

    %!!! [swe]
    \CVHEADING{COMP3900 -- Computer Science Project}{Feb 2022 -- May 2022}
    \startitemize
        \item Revamped "GitLab Team Management" Django project with full-stack boilerplate and upskilled team on Django framework.
        \item Implemented SSO with GitLab web service using django-oidc, GitLab API calls on top of requests library, text search with django-haystack, and object-level permissions with django-rules.
    \stopitemize

    %!!! [swe]
    \CVHEADING{MTRN4110 -- Robot Design}{May 2021 -- Sep 2021}
    \startitemize
        \item Architected robot software for a maze-solving robot with autonomous navigation using world imaging data processed with OpenCV.
        \item Hacked Webots build platform to simultaenously execute C++ and Python programs with Cython interface.
    \stopitemize

    %!!! [swe]
    \CVHEADING{MTRN3500 -- Computing Applications in Mechatronics Systems}{May 2020 -- Sep 2020}
    \startitemize
        \item Developed multi-process application for LiDAR and GNSS processing, and teleoperation of a robot using shared memory IPC.
        \item Built TCP/IP client with WinSock2 to connect to robot over WiFi.
        \item Implemented GUI to visualise robot data processing and motion using OpenGL.
    \stopitemize

    \CVHEADING{COMP1531 -- Software Engineering Fundamentals}{Feb 2020 -- May 2020}
    \startitemize
        \item Developed back-end and API in Flask/Python for a Slack-like application achieving a project mark of 97.
    \stopitemize

%!!! [swe]
\CVSECTION{Achievements}
    \startitemize
        \item UNSW Dean's Honours List. \hfill {\bf 2021}
        \item UNSW Dean's Honours List. \hfill {\bf 2020}
        \item UNSW Dean's Honours List. \hfill {\bf 2019}
        \item New Colombo Plan Scholarship Recipient. \hfill {\bf 2018}
        \item RACI NSW Schools Titration Competition -- Silver Award. \hfill {\bf 2017}
        \item Corporal of Australian Army Cadets. \hfill {\bf 2016}
    \stopitemize

\CVSECTION{Technical Skills}
    \startmixedcolumns[n=2, balance=yes]
        %!!! [swe]
        \CVHEADING{Robotics development}{}
        \startitemize
            \item ROS1/2, RViz, Gazebo.
            \item Webots.
            \item URDF, SDF.
            \item Low-level C/C++14.
            \item C++20 (Catch2, GoogleTest, doctest, GoogleBenchmark, CxxTest).
            \item Assembly (MIPS).
            \item MATLAB (Simulink).
        \stopitemize

        %!!! [swe]
        \CVHEADING{Full Stack App Development}{}
        \startitemize
            \item HTML, CSS, JS, TS.
            \item React (Mantine UI, Chakra UI, React Hook Form, React Query, SWR, Wouter, Zustand).
            \item PostgreSQL, PL/pgSQL.
            \item Firebase (Hosting, Firestore).
            \item Flutter (Provider, Bonsoir).
            \item AWS (Amplify, EC2, S3).
            \item Nginx.
        \stopitemize

        %!!! [swe]
        \CVHEADING{Machine Learning}{}
        \startitemize
            \item Google ML Kit.
            \item TensorFlow (Lite).
        \stopitemize

        %!!! [swe]
        \CVHEADING{Other Programming Languages}{}
        \startitemize
            \item Python <=3.9 (Jupyter, OpenCV).
            \item Java 17 (OOP, design patterns).
        \stopitemize

        %!!! [swe]
        \CVHEADING{Software Tools}{}
        \startitemize
            \item git.
            \item GitHub (Actions, Classroom).
            \item GitLab.
            \item VSCode, Visual Studio.
            \item WSL, Ubuntu, Debian, Windows 10, Mac.
            \item Docker.
        \stopitemize

        %!!! [swe]
        \CVHEADING{Engineering Skills}{}
        \startitemize
            \item Design thinking.
            \item Concept generation & evaluation.
            \item Prototyping.
            \item Project planning & management.
        \stopitemize

        \CVHEADING{Mechanical \& Manufacturing}{}
        \startitemize
            \item 3D CAD (Solidworks, Autodesk Inventor Professional, Fusion360).
            \item Manual metal machining (Lathe, Mill).
            \item 3D-printing.
            \item Laser cutting (Trotec).
            \item Water jet cutting (ProtoMAX).
        \stopitemize

        \CVHEADING{Office}{}
        \startitemize
            \item Microsoft Office (Outlook, Word, Excel, PowerPoint, Teams, SharePoint, Planner, Forms).
            \item \LaTeX, \ConTeXt.
            \item Markdown (Mermaid, GitLab Flavoured).
        \stopitemize
    \stopmixedcolumns

\CVSECTION{Certifications}
    \CVHEADING{Salesforce Platform App Builder}{July 2024}

    \CVHEADING{TAFE Statement in UNSW Engineering Mechanical}{Nov 2019}
    \startitemize
        \item Use Hand Tools.
        \item Use Workshop Machines for Basic Operation.
    \stopitemize

% \CVSECTION{Referees}
%     \startitemize
%         \sym{} {\bf Dr Leo Wu}
%         \sym{} Lecturer, UNSW
%         \sym{} Room 301C, Ainsworth Building J17
%         \sym{} \LINK{liao.wu@unsw.edu.au}{mailto:liao.wu@unsw.edu.au}
%         \sym{} +61 (2) 9385 6548
%     \stopitemize

\stoptext