\usemodule[m-cv]

\starttext

\CVTITLE{Dan Huy}{Nguyen}
\CVSUBTITLE{\LINK{danhuynguyen1@gmail.com}{mailto:danhuynguyen1@gmail.com} \| 0421 720 990 \| \LINK{LinkedIn}{https://www.linkedin.com/in/dan-nguyen-857282190/} \| \LINK{GitLab}{https://gitlab.com/dennuguyen} \| \LINK{GitHub}{https://github.com/dennuguyen} }

\CVSECTION{Education}
    \CVHEADING{University of New South Wales}{Feb 2018 -- April 2024}
        \CVSUBHEADING{Bachelor of Engineering (Hons) (Mechatronics) / Bachelor of Science (Computer Science)}{}
        \startitemize
            \item Graduated 1st class with total weighted average mark of 82.622.
        \stopitemize

\CVSECTION{Work Experience}
    \CVHEADING{Accenture}{}
        \CVSUBHEADING{Application Development Analyst}{May 2024 -- Current}
        \startitemize
            \item Configuring and testing CRM in public sector with Salesforce and Azure DevOps.
        \stopitemize

    \CVHEADING{UNSW}{}
        \CVSUBHEADING{Casual Academic}{Sep 2021 -- Current}
        \startitemize
            \item Involved in planning course curriculum and content from assessments to lectures for C++ and robotics courses across all year levels.
            \item Taught and mentored classes, ran help sessions, and marking for engineering design, robotics, and C++ courses.
            \item Lead migration for delivery of course content using GitHub Classrooms.
            \item Optimise processes using scripting, build tools, CI/CD tools.
            \item List of courses taught for: DESN1000, DESN2000, MTRN2500, MTRN3100, MTRN4110, COMP9024.
            \item List of courses administrated for: MTRN2500, MTRN3100, MTRN4231.
        \stopitemize

\CVSECTION{Project Experience}
    \CVHEADING{Social Media App}{August 2024 -- Current}
        \CVSUBHEADING{Fullstack Developer}{}
        \startitemize
            \item Designed social media mobile app that is cross between popular Dress To Impress Roblox game and BeReal.
            \item Implemented with Flutter + Firebase (Functions, Firestore, Storage, Authentication, AppCheck), Google & Apple social authentication, and custom camera and gallery picker.
        \stopitemize

    \CVHEADING{TV Mate}{May 2024 -- June 2024}
        \CVSUBHEADING{Application Developer}{}
        \startitemize
            \item Designed and implemented Flutter MacOS and iOS app with mDNS-enabled IR-firing IoT devices (ESP8266) for remote control of multiple TVs via websockets over LAN.
            \stopitemize

    \CVHEADING{Split Payment App}{Sep 2023 -- Current}
        \CVSUBHEADING{Application Developer}{}
        \startitemize
            \item Solely prototyping multiplayer split-payment app with fractional splitting enabled by multi-range sliders and OCR for receipt-digitisation.
            \item Built with Firebase, Firestore, React, Mantine UI, Tabler, immer, react-slider, tesseract.js, wouter, zustand, Vite, Vitest.
        \stopitemize

\CVSECTION{Competition Experience}
    \CVHEADING{WIESoc x IBM Hackathon}{Oct 2020}
    \startitemize
        \item Developed prize-winning "COVID Safe Link" website in Flask/Python connecting to Google Maps API and NSW Open Data Platforms to plan safe travel through populated areas and public transport.
    \stopitemize

\CVSECTION{Academic Projects}
    \CVHEADING{MMAN4010/4020 -- Thesis A/B}{May 2023 -- Dec 2023}
    \startitemize
        \item Lead team of students to build proof-of-concept website for real client to achieve course marks of 95 and 89.
        \item Architected system which was website integrated with mechatronic system to automate control of multiple TVs using websockets over WiFi.
    \stopitemize

    \CVHEADING{COMP6080 -- Web Front-End Programming}{May 2023 -- Dec 2023}
    \startitemize
        \item Built frontend Airbnb clone (using React, Mantine, SWR, Axios, Wouter, Zustand) given backend API to achieve course mark of 90.
        \item Built frontend web messaging platform (in pure vanilla JS, HTML, CSS, and Bootstrap) given backend API and using Web APIs like HTML DOM, Intersection Observer, and Navigation.
    \stopitemize

    \CVHEADING{COMP3900 -- Computer Science Project}{Feb 2022 -- May 2022}
    \startitemize
        \item Revamped "GitLab Team Management" Django project with full-stack boilerplate and upskilled team on Django framework.
        \item Implemented SSO with GitLab web service using django-oidc, GitLab API calls on top of requests library, text search with django-haystack, and object-level permissions with django-rules.
    \stopitemize

    \CVHEADING{MTRN4110 -- Robot Design}{May 2021 -- Sep 2021}
    \startitemize
        \item Architected robot software for maze-solving robot with autonomous navigation using world imaging data processed with OpenCV.
        \item Hacked Webots build platform to simultaneously execute C++ and Python programs with Cython interface.
    \stopitemize

    \CVHEADING{MTRN3500 -- Computing Applications in Mechatronics Systems}{May 2020 -- Sep 2020}
    \startitemize
        \item Developed multi-process application for LiDAR and GNSS processing, and teleoperation of robot using shared memory IPC.
        \item Built TCP/IP client with WinSock2 to connect to robot over WiFi.
        \item Implemented GUI to visualise robot data processing and motion using OpenGL.
    \stopitemize

    \CVHEADING{COMP1531 -- Software Engineering Fundamentals}{Feb 2020 -- May 2020}
    \startitemize
        \item Developed back-end and API in Flask/Python for Slack-like application achieving project mark of 97.
    \stopitemize

\CVSECTION{Achievements}
    \startitemize
        \item UNSW Dean's Honours List. \hfill {\bf 2021}
        \item UNSW Dean's Honours List. \hfill {\bf 2020}
        \item UNSW Dean's Honours List. \hfill {\bf 2019}
        \item New Colombo Plan Scholarship Recipient. \hfill {\bf 2018}
    \stopitemize

\CVSECTION{Technical Skills}
    \startmixedcolumns[n=2, balance=yes]
        \CVHEADING{Robotics development}{}
        \startitemize
            \item ROS1/2, RViz, Gazebo.
            \item Webots.
            \item URDF, SDF.
            \item Low-level C/C++14.
            \item C++20 (Catch2, GoogleTest, doctest, GoogleBenchmark, CxxTest).
            \item Assembly (MIPS).
            \item MATLAB (Simulink).
        \stopitemize

        \CVHEADING{Full Stack App Development}{}
        \startitemize
            \item HTML, CSS, JS, TS.
            \item React.
            \item PostgreSQL, PL/pgSQL.
            \item Firebase (Authentication, Functions, Hosting, Firestore, Storage).
            \item Flutter.
            \item AWS (Amplify, EC2, S3).
            \item Nginx.
        \stopitemize

        % \CVHEADING{Machine Learning}{}
        % \startitemize
        %     \item Google ML Kit.
        %     \item TensorFlow (Lite).
        % \stopitemize

        \CVHEADING{Other Programming Languages}{}
        \startitemize
            \item Python <=3.9 (Jupyter, OpenCV).
            \item Java 17 (OOP, design patterns).
        \stopitemize

        \CVHEADING{Software Tools}{}
        \startitemize
            \item git.
            \item GitHub (Actions, Classroom).
            \item GitLab.
            \item VSCode, Visual Studio.
            \item WSL, Ubuntu, Debian, Windows 10, Mac.
            \item Docker.
        \stopitemize

        \CVHEADING{Engineering Skills}{}
        \startitemize
            \item Design thinking.
            \item Concept generation & evaluation.
            \item Prototyping.
            \item Project planning & management.
        \stopitemize
    \stopmixedcolumns

\stoptext